### 2020-01-29 ChapterResults/chapterResults.tex
Added: Subsection on thrashing in results with histogram

>>>>

\subsection{Thrashing}
In addition to recording the number of collisions that resulted in thrashing, the number of times an object thrashed between servers was also measured. The number of times thrashed is determined by measuring the number of migrations away from the server that the collisions takes place on, before the collision takes place. A histogram of the number of occurrences against the number of times thrashed is shown in Fig. \ref{fig_ThrashingHistogram}. For this histogram, data from the Frame-Time $33.33ms$ experiment is used, as this provides the largest sample of thrashing. As is demonstrated in Fig. \ref{fig_ThrashingHistogram}, the most frequent number of times thrashed is 1, by a large margin followed by a downward trend.

The more times thrashing occurs, the later the collision may be detected as objects continue to be updated and move without a collision occurring. It should be noted that thrashing occurring does not guarantee that a late collision will take place. The more times thrashing takes place, the more physics updates occur and the further the objects may be moved towards (and eventually overlapping) each other. Therefore, a greater number of times thrashed, means a late and incorrect collision response is more likely.

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{ThrashingHistogram}
	\caption{Thrashing Histogram. The number of occurrences vs the number of times thrashed.}
	\label{fig_ThrashingHistogram}
\end{figure}
